---
title: "Gapminder"
author: "DR"
date: "11/03/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gapminder)
library(tinytex)
```

## Introduction

In this document we will be exploring the Gapminder dataset

## Observations of Gapminder

### Countries with life expectancy less than 30

```{r gapminder,echo=FALSE}
data(gapminder)
life_exp_under_30 <- gapminder %>% filter(lifeExp <= 30)
life_exp_under_30
```

There are only **3 countries** with lifeexp *less than 30*

These countries are:
- all in 1952
- mainly in Africa

### Countries with life expectancy greater than 81

```{r gapminder2, echo=FALSE}
data(gapminder)
life_exp_over_81 <- gapminder %>% filter(lifeExp >= 81)
life_exp_over_81
```

There are only *5 countries** across 7 years with lifeexp _greater than 81_

These countries are:
- mainly in Australasia
- some in Europe
- in this millenium

### Life Expectancy by continent in 2007
```{r gapminder3, echo=FALSE}
life_exp_07 <- gapminder %>% filter(year == 2007)
boxplot(lifeExp~continent, data = life_exp_07)

```

**Africa** has by far the *lowest* life expectancy.

**Oceania** has by far the *highest*. This may be due to less countries^2^. We should explore this further.
